Comparison of Catalogs

### 2024-10-05 compare/compare.tex
def and expl

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{luacolor}
  \usepackage[soul]{lua-ul}
\else
  \usepackage{soul}

\fi
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

In this script we will compare 2 catalogs Kovlakas et al. (2021) and
Karachentsev and Kaisina (2013)

@@

Checking for completeness in galaxy catalogs is essential to ensure that
the data accurately represents the true population of galaxies.
Incomplete catalogs can lead to biased results in statistical studies,
such as the distribution of galaxy luminosity, mass, or star formation
rates. Additionally, missing galaxies, especially those at faint
magnitudes or large distances, can distort cosmological measurements and
hinder our understanding of galaxy formation and evolution.

@@

The local volume selection has been made by taking into account galaxies
with: 1. Radial velocities of
\begin{equation}\phantomsection\label{eq-lcv-vel}{
    V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
    }\end{equation} 2. Distances of D\textless11 Mpc

@@

\begin{itemize}
\tightlist
\item
  Completeness within a 10 Mpc radius is difficult to assess due to:

  \begin{itemize}
  \tightlist
  \item
    Variability in galaxy properties (luminosity, size, surface
    brightness, gas content)
  \item
    Errors in distance measurements (Tully--Fisher method errors of
    \textasciitilde20--25\%), especially at the 10 Mpc boundary.

    \begin{itemize}
    \tightlist
    \item
      Accurate distances are mainly known within \textasciitilde5 Mpc.
    \end{itemize}
  \item
    Non-Hubble motions (\textasciitilde300 km/s) may make up half of the
    adopted velocity constraint Equation~\ref{eq-lcv-vel}

    \begin{itemize}
    \tightlist
    \item
      Solution for our usage: only keep the galaxies inside a radius of
      \(D=11 Mpc\)
    \item
      HI sources in surveys with low angular resolution: ``The presence
      around our Galaxy of hundreds of high-velocity clouds with low
      line-of-sight velocities and small W50 widths also provokes the
      inclusion of false ``nearby'' dwarf galaxies in the
      LV''Karachentsev, Makarov, and Kaisina (2013)
    \item
      photographic emulsion defect -\textgreater{} exotic cases of
      galaxies -\textgreater{} radial velocity of \(+614 km s^{−1}\)
    \end{itemize}
  \end{itemize}
\item
  Astro-Spam and Survey Errors:

  \begin{itemize}
  \tightlist
  \item
    Automatic surveys produce false detections (e.g., stars
    misclassified as galaxies, high-velocity clouds mistaken for
    dwarfs).
  \end{itemize}
\item
  Conditional Completeness Estimate:

  \begin{itemize}
  \tightlist
  \item
    Galaxies brighter than \(M_B^c = -11^m\) or with linear diameters
    larger than \(A_{26} = 1.0\) kpc show (40--60)\% completeness.
  \item
    ``among the members of the Local Group (D \textless{} 1 Mpc), only
    half of the galaxies have absolute magnitudes brighter than −11m.
    Consequently, more than half of the ultra-faint dwarf companions
    around normal galaxies, like the Sombrero galaxy (D = 9.3 Mpc),
    still remain outside our field of view.''
  \end{itemize}
\item
  Undetected Ultra-Faint Dwarfs:

  \begin{itemize}
  \tightlist
  \item
    Many faint dwarf galaxies remain undetected beyond the Local Group.
    Estimated population of undetected dwarfs could be as large as
    \(10^3–10^4\) within the LV.
  \end{itemize}
\item
  Surface Brightness Distribution:

  \begin{itemize}
  \tightlist
  \item
    Surface brightness remains consistent across distances, except for
    ultra-faint dwarfs (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)).
  \item
    Faintest dwarf galaxies are detectable only nearby due to their
    resolution into individual stars.
  \end{itemize}
\item
  Luminosity-Size Relationship:

  \begin{itemize}
  \tightlist
  \item
    Observations align with cosmological models predicting \(L\sim A^3\)
    Navarro, Frenk, and White (1996), though deviations occur for
    extremely low surface brightness galaxies.
  \item
    ``The deviation from it at the extremely low surface brightness end
    is due to a systematic overestimation of dwarf galaxy sizes, the
    brightness profiles of which lie entirely below the Holmberg
    isophote.''
  \end{itemize}
\end{itemize}

@@

\subsubsection{Distance}\label{distance}

@@

As we can see from the histograms Figure~\ref{fig-dis-comp} and
Figure~\ref{fig-type-comp} the sample of unique galaxies of each
catalog, gets smaller by an almost constant proportion (Inner join).

@@

\subsection{\texorpdfstring{Scatter plots and \(R^2\)
calculation}{Scatter plots and R\^{}2 calculation}}\label{scatter-plots-and-r2-calculation}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(R^2\): Measures the proportion of variance explained by the linear
  model.
\item
  Slope of the Fitted Line: Should be close to 1 for a 1-1
  correlation.\footnote{Some data seem to have a very good linear
    correlation but they have many outliers. This is why we will clip
    the outliers with \(\sigma > 3\)}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Pearson Correlation \(\rho\): Measures the strength and direction of
  the linear relationship between two variables, ranging from -1 to 1.
  \footnote{In simple linear regression, \(R^2\) is the square of the
    Pearson correlation coefficient \(\rho\).}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  \ul{Plots}: Plots are essential for visually assessing the
  relationship between two datasets, identifying correlations, trends,
  and outliers, and evaluating the fit of linear models.
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Histograms: Because not all of our data have the same number of
  counts, the comparison with histograms between data that are not the
  same, doesn't help us right now.\footnote{When we will use the outer
    join table we could use histograms due to the large number of
    counts.} This is why we will only use histograms for comparing the
  distribution of same-data columns normalized by their maximum value
\end{itemize}

\begin{itemize}
\item
  Correlation Heatmaps: A correlation heatmap is a graphical tool that
  displays the correlation between multiple variables as a color-coded
  matrix. It's like a color chart that shows us how closely related
  different variables are. In a correlation heatmap, each variable is
  represented by a row and a column, and the cells show the correlation
  between them. The color of each cell represents the strength and
  direction of the correlation, with darker colors indicating stronger
  correlations.
\item
  Kernel Density Estimate (KDE) plot: The KDE plot visually represents
  the distribution of data, providing insights into its shape, central
  tendency, and spread.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  Percentage change: We can calculate the percentage change of the data
  for each galaxy and then we can see if the data are similar, based on
  minimum, the maximum and the mean value of the difference.
\end{enumerate}

@@

\begin{longtable}[]{@{}cccc@{}}
\toprule\noalign{}
LCV & HECATE & Description & Pearson Correlation {[}-1,1{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Dis & D & Distance & 0.881 \\
\end{longtable}

@@

\begin{itemize}
\tightlist
\item
  The average error of the distance in the HECATE catalog is
  \(\overline{E_D} = \pm 1.6\) Mpc, so the intercept is included in the
  error.
\item
  So we can assume that the Distances are the same
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The average error of the radial velocity in the HECATE catalog is
  \(\overline{E_V} = \pm 12\text{km}\cdot s^{-1}\) , so the intercept is
  included in the error.
\item
  So we can assume that the radial velocities are the same
\end{itemize}

\includegraphics{compare_files/figure-pdf/cell-15-output-1.pdf}

@@

@@

@@

``Morphological type of galaxy in the numerical code according to the
classification by de Vaucouleurs et al.~(1991). It should be noted that
about three quarters of objects in the LV are dwarf galaxies, which
require a more detailed morphological classification. For example, dwarf
spheroidal galaxies and normal ellipticals are usually denoted by the
same numerical code T \textless{} 0, although their physical properties
drastically differ. The classification problem arises as well for the
``transient'' type dwarf galaxies, T r, which combine the features of
spheroidal (Sph) and irregular (Ir)systems. Due to small classification
errors, such objects may ``jump'' from one end of the T scale to the
other.'' Karachentsev, Makarov, and Kaisina (2013)

\begin{itemize}
\tightlist
\item
  we can assume that the galaxies from the upper left and lower right
  regions of the plot are classified differently because of this
\item
  this might explain the large errors E\_T of HECATE
\item
  why we see a difference in the distribution of
  Figure~\ref{fig-type-comp}
\end{itemize}

We can remove the ``problematic'' galaxies by only keeping the ones
with: \[
|{T_{HECATE}-T_{LCV}}|<7
\]

\begin{itemize}
\tightlist
\item
  The average uncertainty of the morphological type in the HECATE
  catalog is \(\overline{E_T} = \pm 1.4\), so the intercept is included
  in the error.
\item
  So we can assume that the Distances are the same
\end{itemize}

@@

\begin{minipage}{0.50\linewidth}
\includegraphics{compare_files/figure-pdf/cell-24-output-1.pdf}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics{compare_files/figure-pdf/cell-24-output-2.pdf}\end{minipage}%

@@

We can see that for values in the range
\([\sim 30^\circ,\sim 80^\circ]\), the values of the LCV inclination are
higher. However, since their means, median, min and maxes are similar
and the percentage change is practically 0\% (mean, median, \(\sigma\) =
0 with a range \([-3\%,1\%]\)), we can ignore the differences and assume
they are the same values.

@@

it is not very clear if we truly have a correlation or not. We need to
see the linear correlation of the decimal logarithms.

\(\overline{R_1} = 3.9\) {[}arcmin{]}, \(\overline{a_{26}} = 9.3\)
{[}arcmin{]}, so the intercept is negligable. \[
R_1 = 0.48\cdot a_{26}-0.34 \sim \frac{1}{2}a_{26}
\]

@@

\caption{\label{fig-klum-compare}Comparison of the \(L_K\) of the
galaxies}

@@

So as we can see the usage of a linear fitting is not correct here. But
we can clearly see a linear correlation.

We will use the relative difference of the two luminosities, to see if
statistically they are the same:

\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
& log(L\_K)\_\{LCV\}\$ & log(L\_K)\_\{HEC\} & Percentage Change
{[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 287 & 70 & 70 \\
mean & 8 & 9 & -4 \\
std & 1 & 1 & 8 \\
min & 3 & 5 & -48 \\
50\% & 8 & 9 & -0 \\
max & 11 & 11 & 7 \\
\end{longtable}

@@

\begin{itemize}
\tightlist
\item
  \(M_B\): it is a 1-1 correlation, since the average error
  \(M_{B,HECATE} = 0.4\ mag\), so the itercept is smaller than the error
\item
  \(M_K\): we need to examine it more, since the intercept is bigger
  than the error \(M_{K,HECATE} = 0.09\ mag\)
\end{itemize}

\includegraphics{compare_files/figure-pdf/cell-35-output-2.pdf}

@@

{[}?{]} this 5\% average in the difference probably exists because of
the low number of galaxies we compare, so we can ignore it.

@@

\caption{\label{fig-sfr-lcv}Comparison of the \$SFR\_\{FUV\}-SFR\_\{Ha\}
of the galaxies}

@@

The SFR according to Kroupa et al. (2020), can be calculated from the
mean of SFR from the Ha and FUV, for \(SFR>10^{-3}\ M_\odot\, yr^{-1}\).
As we can see from the plots Figure~\ref{fig-sfr-lcv} it is a good
aproximation for all SFR's

@@

?EXPLANATION? this low correlation maybe comes from the
inaccuracy/approximation of Kroupa et al. (2020)

@@

\includegraphics{compare_files/figure-pdf/cell-44-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-45-output-1.pdf}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-karachentsevSTARFORMATIONPROPERTIES2013a}
Karachentsev, Igor D., and Elena I. Kaisina. 2013. {``{STAR FORMATION
PROPERTIES IN THE LOCAL VOLUME GALAXIES VIA Hα AND FAR-ULTRAVIOLET
FLUXES}.''} \emph{The Astronomical Journal} 146 (3): 46.
\url{https://doi.org/10.1088/0004-6256/146/3/46}.

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmainfont[]{Latin Modern Roman}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

In this script we will compare 2 catalogs, HECATE (Kovlakas et al.
(2021)) and LCV (Karachentsev and Kaisina (2013))

@@

Checking for completeness in galaxy catalogs is essential to ensure that
the data accurately represents the true population of galaxies, for
\(z \approx 0\). Incomplete catalogs can lead to biased results in
statistical studies, such as the distribution of galaxy luminosity,
mass, or star formation rates. Additionally, missing galaxies,
especially those at faint magnitudes or large distances, can distort
cosmological measurements and hinder our understanding of galaxy
formation and evolution.

@@

The local volume selection has been made by taking into account galaxies
with:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Radial velocities of
  \begin{equation}\phantomsection\label{eq-lcv-vel}{
   V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
  }\end{equation}
\item
  Distances of \begin{equation}\phantomsection\label{eq-lcv-dis}{
     D<11\ \text{Mpc}
     }\end{equation}
\end{enumerate}

@@

\subsubsection{Difficulties in calculating the
Completeness}\label{difficulties-in-calculating-the-completeness}

As explained in (Karachentsev, Makarov, and Kaisina (2013)), it is
difficult to calculate the completeness of the catalog.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Completeness within a 10 Mpc radius is difficult to assess due to: -
  Variability in galaxy properties (luminosity, size, surface
  brightness, gas content) - Errors in distance measurements
  (Tully--Fisher method errors of \textasciitilde20--25\%), especially
  at the 10 Mpc boundary.

  \begin{itemize}
  \tightlist
  \item
    Accurate distances are mainly known within \textasciitilde5 Mpc.
  \item
    Non-Hubble motions (\textasciitilde300 km/s)\footnote{\emph{Non-Hubble
      motion refers to the component of a galaxy's velocity that
      deviates from the uniform expansion of the universe, described by
      the equation} \(V= H_0 d + v_p\),where \(V\) is the total
      velocity, \(H_0 d\) represents the Hubble flow, and
      \(v_p\)\hspace{0pt} is the peculiar velocity. {``Essay''} (n.d.)}
    may make up half of the adopted velocity constraint
    (Equation~\ref{eq-lcv-vel})
  \item
    Solution for our usage: only keep the galaxies inside a radius of
    \(D=11 Mpc\)
  \item
    HI sources in surveys with low angular resolution: ``The presence
    around our Galaxy of hundreds of high-velocity clouds with low
    line-of-sight velocities and small W50 widths also provokes the
    inclusion of false ``nearby'' dwarf galaxies in the
    LV''(Karachentsev, Makarov, and Kaisina (2013))
  \end{itemize}
\item
  Astro-Spam and Survey Errors: - Automatic surveys produce false
  detections (e.g., stars misclassified as galaxies, high-velocity
  clouds mistaken for dwarfs).
\item
  Conditional Completeness Estimate: - Galaxies brighter than
  \(M_B^c = -11^m\) or with linear diameters larger than
  \(A_{26} = 1.0\) kpc show (40--60)\% completeness. - ``among the
  members of the Local Group (D \textless{} 1 Mpc), only half of the
  galaxies have absolute magnitudes brighter than −11m. Consequently,
  more than half of the ultra-faint dwarf companions around normal
  galaxies, like the Sombrero galaxy (D = 9.3 Mpc), still remain outside
  our field of view.''
\item
  Undetected Ultra-Faint Dwarfs: - Many faint dwarf galaxies remain
  undetected beyond the Local Group. Estimated population of undetected
  dwarfs could be as large as \(10^3–10^4\) within the LV.
\item
  Surface Brightness Distribution: - Surface brightness remains
  consistent across distances, except for ultra-faint dwarfs
  (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)). - Faintest dwarf
  galaxies are detectable only nearby due to their resolution into
  individual stars.
\item
  Luminosity-Size Relationship: - Observations align with cosmological
  models predicting \(L\sim A^3\) (Navarro, Frenk, and White (1996)),
  though deviations occur for extremely low surface brightness galaxies.
  - ``The deviation from it at the extremely low surface brightness end
  is due to a systematic overestimation of dwarf galaxy sizes, the
  brightness profiles of which lie entirely below the Holmberg
  isophote.''
\end{enumerate}

@@

@@

As we can see from the histograms (Figure~\ref{fig-dis-comp}) and
(Figure~\ref{fig-type-comp}) the sample of unique galaxies of each
catalog, gets smaller by an almost constant proportion (Inner join).

@@

For the comparison of our data we will mainly use two methods: linear
regression and comparison of the distributions.

For the linear regression out main tools are scatter plots and \(R^2\)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \(R^2\): Measures the proportion of variance explained by the linear
  model.
\item
  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.
\item
  Pearson Correlation \(\rho\): Measures the strength and direction of
  the linear relationship between two variables, ranging from -1 to 1.
  \footnote{In simple linear regression, \(R^2\) is the square of the
    Pearson correlation coefficient \(\rho\).}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\item
  Plots: Plots are essential for visually assessing the relationship
  between two datasets, identifying correlations, trends, and outliers,
  and evaluating the fit of linear models. Beside scatter plots and
  histograms, another useful plot is the Correlation Heatmap.

  \begin{quote}
  Correlation Heatmaps: A correlation heatmap is a graphical tool that
  displays the correlation between multiple variables as a color-coded
  matrix. It's like a color chart that shows us how closely related
  different variables are. In a correlation heatmap, each variable is
  represented by a row and a column, and the cells show the correlation
  between them. The color of each cell represents the strength and
  direction of the correlation, with darker colors indicating stronger
  correlations.
  \end{quote}
\end{enumerate}

For the distrabution comparisons we will use histograms and Kernel
Density Estimate (KDE) plots. The KDE plots visually represent the
distribution of data, providing insights into its shape, central
tendency, and spread.

Finally, we will examine the percentage change for each galaxy.

\begin{itemize}
\tightlist
\item
  Percentage change: We can calculate the percentage change of the data
  for each galaxy and then we can see if the data are similar, based on
  minimum, the maximum and the mean value of the difference.
\end{itemize}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3014}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pearson Correlation {[}-1,1{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Dis & D & Distance & 0.881 \\
\end{longtable}

@@

\begin{itemize}
\tightlist
\item
  The average error of the distance in the HECATE catalog is
  \(\overline{\delta D} = \pm 1.6\) Mpc, so the intercept is included in
  the error.
\item
  So we can assume that the Distances are the same
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The average error of the radial velocity in the HECATE catalog is
  \(\overline{\delta V} = \pm 12\text{km}\cdot s^{-1}\) , so the
  intercept is included in the error.
\item
  So we can assume that the radial velocities are the same
\end{itemize}

\includegraphics{compare_files/figure-pdf/fig-vel-pairplot-output-1.pdf}

\caption{\label{fig-vel-pairplot}The correlation Matrix of the
Velocities. The lower left triangle is is composed of the scatter plots
of the various velocities, the diagonal shows their distrubution and the
upper right triangle shows the correlations of the Velocities}

@@

The strong correlation between the velocities reported by the HECATE and
LCV catalogs can be attributed to the fact that both measure the same
intrinsic galaxy velocities but reference them to different frames. For
instance, velocities can be corrected for the movement of the Earth
(heliocentric frame) or the for the Virgo-infall. These corrections
shift the measured velocity slightly, but the fundamental measurement
remains consistent. This explains why the velocities are highly
correlated, as they represent the same physical phenomenon but adjusted
for different reference points.

\newpage{}

@@

``Morphological type of galaxy in the numerical code according to the
classification by de Vaucouleurs et al.~(1991). It should be noted that
about three quarters of objects in the LV are dwarf galaxies, which
require a more detailed morphological classification. For example, dwarf
spheroidal galaxies and normal ellipticals are usually denoted by the
same numerical code T \textless{} 0, although their physical properties
drastically differ. The classification problem arises as well for the
``transient'' type dwarf galaxies, T r, which combine the features of
spheroidal (Sph) and irregular (Ir)systems. Due to small classification
errors, such objects may ``jump'' from one end of the T scale to the
other.'' (Karachentsev, Makarov, and Kaisina (2013))

@@

\begin{itemize}
\tightlist
\item
  we can assume that the galaxies from the upper left and lower right
  regions of the plot are classified differently because of this
\item
  this might explain the large errors E\_T of HECATE
\item
  why we see a difference in the distribution of
  (Figure~\ref{fig-type-comp})
\end{itemize}

We can remove the ``problematic'' galaxies by only keeping the ones
with: \[
|{T_{HECATE}-T_{LCV}}|<\sigma_{T_{LCV}} = 4.8
\]

\begin{itemize}
\tightlist
\item
  The average uncertainty of the morphological type in the HECATE
  catalog is \(\overline{\delta T} = \pm 1.4\), so the intercept is
  included in the error.
\item
  So we can assume that the Distances are the same
\end{itemize}

@@

\includegraphics{compare_files/figure-pdf/fig-incl-compare-output-1.pdf}

\subcaption{\label{fig-incl-compare-1}Distribution of the Inclination of
the galaxies}

\includegraphics{compare_files/figure-pdf/fig-incl-compare-output-2.pdf}

\subcaption{\label{fig-incl-compare-2}Distribution of the Percentage
Change}

\caption{\label{fig-incl-compare}Comparison of the Inclination of the
galaxies}

@@

We can see that for values in the range
\([\sim 30^\circ,\sim 80^\circ]\), the values of the LCV inclination are
higher (Figure~\ref{fig-incl-compare}). However, since their means,
median, min and maxes are similar and the percentage change is
practically 0\% (mean, median, \(\sigma\) = 0 with a range
\([-3\%,1\%]\)), we can ignore the differences and assume they are the
same values.

@@

it is not very clear if we truly have a correlation or not
(Figure~\ref{fig-axis-compare-1}). We need to see the linear correlation
of the decimal logarithms (Figure~\ref{fig-axis-compare-2}).

\(\overline{R_1} = 3.9\) {[}arcmin{]}, \(\overline{a_{26}} = 9.3\)
{[}arcmin{]}, so the intercept is negligable.

\[
R_1 = 0.48\cdot a_{26}-0.34 \sim \frac{1}{2}a_{26}
\]

@@

\subcaption{\label{fig-klum-compare-1}Linear Regression with free
paramaters, \(y=ax+b\)}

\includegraphics{compare_files/figure-pdf/fig-klum-compare-output-2.pdf}

\subcaption{\label{fig-klum-compare-2}Linear Regrassion \(y=x\)}

\caption{\label{fig-klum-compare}Comparison of the \(L_K\) of the
galaxies.}

@@

To assess whether the two galaxy catalogs have a 1-1 correlation, I
applied two types of linear fits to the data: a free fit and a forced
fit. The free fit allows both the slope and intercept to vary freely,
meaning the line can take on any slope and can cross the y-axis at any
point. In contrast, for the forced fit, I set the slope to exactly 1 and
fixed the line to pass through the origin, meaning the equation becomes
y=xy=x. This forced fit represents a perfect 1-1 relationship, where the
values from one catalog should match the other exactly, without any
shift or scaling.

After fitting the data using both methods, I calculated the \(R^2\)
value for each fit. In this case, both the free fit and the forced fit
produced very similar \(R^2\) values, around 87.13\%\footnote{The
  difference of the linear regression with the free parameters and the
  forced regression is \(\Delta R^2 = 1.14\cdot 10^{-13}\%\)},
indicating that both fits explain about 87\% of the variance in the data
(Figure~\ref{fig-klum-compare}).

The fact that both the free and forced fits have nearly identical
\(R^2\) values suggests that the data closely follows a 1-1
relationship. In the free fit, the best-fitting line had a very small
intercept, which shows that allowing the line to shift vertically did
not significantly improve how well the line fits the data. This strongly
indicates that the data from the two catalogs are well-aligned and
follow the relationship y=x quite closely, which is what we expect if
the catalogs are in good agreement.

While these results are promising, it's important to note that achieving
an \(R^2\) of 87\%---while high---doesn't necessarily prove a perfect
1-1 correlation. There may still be small discrepancies or uncertainties
in the data that prevent a perfect match. Nonetheless, the fact that
fixing the slope to 1 and forcing the line through the origin gave such
a good result suggests that the two catalogs are very consistent with
each other.

@@

\begin{itemize}
\tightlist
\item
  \(M_B\): it is a 1-1 correlation, since the average error
  \(M_{B,HECATE} = 0.4\ mag\), so the itercept is smaller than the error
  (Figure~\ref{fig-mag-compare})
\item
  \(M_K\): we need to examine it more, since the intercept is bigger
  than the error \(M_{K,HECATE} = 0.09\ mag\)
  (Figure~\ref{fig-mag-compare})
\end{itemize}

\includegraphics{compare_files/figure-pdf/cell-26-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-26-output-2.pdf}

@@

{[}?{]} this 5\% mean in the difference probably exists because of the
low number of galaxies we compare, so we can ignore it.

@@

\caption{\label{fig-sfr-lcv}Comparison of the \(SFR_{FUV}-SFR_{Ha}\) of
the galaxies}

@@

The SFR according to (Kroupa et al. (2020)), can be calculated from the
mean of SFR from the Ha and FUV, for \(SFR>10^{-3}\ M_\odot\, yr^{-1}\).
As we can see from the plots (Figure~\ref{fig-sfr-lcv}) it is a good
aproximation for all SFR's

@@

{[}?{]}EXPLANATION this low correlation maybe comes from the
inaccuracy/approximation of (Kroupa et al. (2020))

The reason is that this aproximation is accurate if we consider a stable
SFR over time. However, we tend to observe higher Ha for more recent SF
activity. (we discussed it in our last meeting, I need a refrence).

@@

@@

The heatmap is used to visually assess the correlations between
different mass estimates of the galaxies, including the mass within the
Holmberg radius (\(M_{26}\)), the HI gas mass (\(M_{HI}\)\hspace{0pt}),
the stellar mass from the HECATE catalog (\(M_{HEC}\)\hspace{0pt}), and
the stellar mass derived assuming a mass-to-light ratio of 0.6
(StellarMass). The purpose of this visualization is to quickly identify
whether these different mass measurements show consistent correlations,
which would suggest that they capture similar aspects of the galaxies'
mass distributions.

This quick check using the heatmap helps confirm that, while different
catalogs and methods might have their own specific ways of calculating
galaxy masses, the overall mass estimates align well, offering a solid
basis for further analysis of galaxy properties.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Essay}
{``Essay.''} n.d. Accessed October 5, 2024.
\url{https://ned.ipac.caltech.edu/level5/Glossary/Essay_pecmotion.html}.

\bibitem[\citeproctext]{ref-karachentsevSTARFORMATIONPROPERTIES2013a}
Karachentsev, Igor D., and Elena I. Kaisina. 2013. {``{STAR FORMATION
PROPERTIES IN THE LOCAL VOLUME GALAXIES VIA Hα AND FAR-ULTRAVIOLET
FLUXES}.''} \emph{The Astronomical Journal} 146 (3): 46.
\url{https://doi.org/10.1088/0004-6256/146/3/46}.
